Estimating individual subjective values of emotion regulation strategies

### 2022-06-28 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted new revision file with design table

\begin{figure}
\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can be represented by our paradigm.}\label{fig:ResponsePatterns}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Design_ER-ED} \caption{Block design of the paradigm. Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures. Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants. After, the discounting procedure takes place. All three regulation strategies are pairwise compared. Before the last block, participants can decide which regulation strategy they want to reapply. Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.}\label{fig:DesignERED}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{ }\label{fig:ResponsePatternsAppendix}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Design_ER-ED} \caption{ }\label{fig:DesignEREDappendix}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can be represented by our paradigm.}\label{fig:ResponsePatterns}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/Design_ER-ED} \caption{Block design of the paradigm. Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures. Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants. After, the discounting procedure takes place. All three regulation strategies are pairwise compared. Before the last block, participants can decide which regulation strategy they want to reapply. Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.}\label{fig:DesignERED}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/Paradigm_Scheme_T2} \caption{ }\label{fig:ResponsePatternsAppendix}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{figures/Design_ER-ED} \caption{ }\label{fig:DesignEREDappendix}
\end{figure}
